### 2013-10-27 src2/thesis.tex
update

When compiling Obsidian programs to CUDA, we only need to be concerned with the 
{\tt Program} datatype. Given the hierarchy level type parameters to the program datatype 
we know that the AST can be quite directly translated to CUDA. We know that there will 
be at most one level of nestedness in the parallelism (several blocks, each of several threads). 
This means that we do not need to do any transformations on the AST before generating CUDA code.

@@

Here and there in the thesis it has been hinted that Obsidian has warp level 
capabilites and that these are not as integrated into the hierarchy as block, 
thread and grid are. The warp abstractions offered also requires more work in 
the code generating backend than the others, that correspond directly to CUDA concepts. 
The problem is that CUDA does not have a warp abstraction. Warps needs to be 
better integrated with the rest of Obsidian and the code generation required 
for warps needs more testing before being trustworthy and useful.

>>>>

When compiling Obsidian programs to CUDA, we only need to be concerned with the 
{\tt Program} datatype. Given the hierarchy level type parameters to the program datatype 
we know that the AST can be quite directly translated to CUDA. We know that there will 
be at most one level of nestedness in the parallelism (several blocks, each of several threads). 
This means that we do not need to do any transformations on the AST before generating CUDA code. 
Paper F (section~\ref{sec:paperF}) contains technical details of the compilation process.

@@

Here and there in the thesis it has been hinted that Obsidian has warp level 
capabilites and that these are not as integrated into the hierarchy as the block, 
thread and grid levels are. The warp abstractions offered also requires more work in 
the code generating backend than the others, that correspond directly to CUDA concepts. 
The problem is that CUDA does not have a warp abstraction. Warps needs to be 
better integrated with the rest of Obsidian and the code generation required 
for warps needs more testing before being trustworthy and useful.
